\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4 in,right=0.4 in,bottom=0.4 in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{ABHIK L SALIAN} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 7411328238 \\ Mangaluru, Karnataka}
\address{\href{mailto:abhiksalian0728@gmail.com}{\textcolor{black}{abhiksalian0728@gmail.com}} \\ \href{https://linkedin.com/in/abhik-salian}{\textcolor{black}{linkedin.com/in/abhik-salian}} \\ \href{https://www.github.com/AbhikSalian}{\textcolor{black}{github.com/AbhikSalian}}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{PROFILE}

{As a Computer Science undergraduate with a consistent academic record,
 I am eager to learn new things every day. 
 I have a solid grasp of key fundamentals of Computer Science topics and 
 I am excited to begin my career by applying my knowledge and skills to 
 real-world projects.
}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Engineering}, St. Joseph Engineering College, Mangaluru \hfill {2021 - 2025(expected)}\\
Computer Science and Engineering, CGPA - 9.47/10

{\bf Higher Secondary}, St. Aloysius PU College, Mangaluru \hfill {2019 - 2021}\\
PCME, Percentage - 98\%

{\bf High School}, St. Aloysius High School, Urwa, Mangaluru \hfill {2009 - 2019}\\
SSLC Percentage - 95.52\%
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & C, Java, Python, HTML, CSS, JavaScript, MySQL, Matlab, PHP, SolidWorks, Ansys
\\
Soft Skills & Adaptability, Interpersonal Communication, Leadership, Punctual, Time Management\\
% Other Skills & UAV Piloting, RC Aircraft and Drone Fabrication\\
\end{tabular}
\end{rSection}

\begin{rSection}{INTERNSHIPS}

\textbf{Web Developer Intern} \hfill Oct 2023 - Nov 2023\\
Glowtouch Technologies Pvt. Ltd. \hfill \textit{Mangaluru, Karnataka}
 \begin{itemize}
    \itemsep -3pt {} 
    %  \item Carried out 4-week internship in the web development domain
     \item Worked on full-stack web projects under the guidance of industry mentors.
    \item Developed a full-stack web application 'SmartStitch', that is designed for the clients of tailors to ease their tailoring process. 
 \end{itemize}
 


\end{rSection} 

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%------------------------------------------------------------------------------------------
\begin{rSection}{Certifications} 
%     \textbf{Salesforce Administrator} \hfill Nov 2023\\
% Certified by SmartInternz %\hfill \textit{Mangaluru, Karnataka}
%  \begin{itemize}
%     \itemsep -3pt {} 
%     %  \item Carried out 4-week internship in the web development domain
%     \item Through the certification, I learned to create and customize reports and dashboards for data analysis and business insights. 
%      \item Developed problem-solving skills to address and resolve common issues within the Salesforce platform.
%  \end{itemize}
    \begin{itemize}
        \item \textbf{Salesforce Administrator} \hfill Nov 2023\\
        Salesforce Administrator Certification validates skills in managing and configuring Salesforce.\\
        Through the certification, I Learned to create and customize reports and dashboards for data analysis and business insights.
    \end{itemize}
    
    
    \end{rSection}
    

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\begin{itemize}
\item \textbf{SmartStitch - A smart application for your tailoring needs}{, is an innovative web platform designed to streamline the process of ordering tailor-made dresses. Clients can easily provide their measurements and place orders without the need to visit a tailor in person.}
% \textbf{Github repository: }\href{https://github.com/AbhikSalian/tailor-database}{\textcolor{black}{https://github.com/AbhikSalian/tailor-database}}}
\item \textbf{WiFi based Intelligent Parking Space}{, Implemented using ESP8266 WiFi Module and Blynk IoT, which manages the empty parking slots in enclosed parking spaces by directing the incoming cars to those slots.}
% \textbf{Github repository: }\href{https://github.com/AbhikSalian/smart-parking-system}{\textcolor{black}{https://github.com/AbhikSalian/smart-parking-system}}}
% \item \textbf{Animal Tracking Device}{, Developed using Arduino, GPS and SIM800L GSM module. Once attached to the animal's body, it sends real-time location of the animal to the owner's phone at regular intervals.}
% \textbf{Github repository: }\href{https://github.com/AbhikSalian/animal-tracking-system}{\textcolor{black}{https://github.com/AbhikSalian/animal-tracking-system}}}
\end{itemize}

\end{rSection}

\begin{rSection}{Extra-Curriculars} 
    \begin{itemize}
        \item 	\textbf{Chief Pilot Trainer} at \textbf{SJEC AERO}, which is the Aeromodelling club of St. Joseph Engineering College, that aims at creating innovation in the field of UAVs.
        % \item	\textbf{Member} at \textbf{GDSC-SJEC}, which is an inclusive developer group powered by Google Developers.
    
    \end{itemize}
    
    
    \end{rSection}

\begin{rSection}{Achievements} 
    \begin{itemize}
        \item 	\textbf{First place} at \textbf{Boeing National Aeromodelling Zonals} held at IIT Bombay on December 28 an 29, 2023.
    \item Participated in \textbf{Prime 2023} at \textbf{SJEC}, which fostered strong entrepreneurial abilities within us.
    \end{itemize}
    
    
    \end{rSection}


\end{document}
